\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-22 tex/overview.tex
state that all networks with certain architectures are unstable

Each distinct labeled directed graph $G$ (of which there are $k=2^{n(n-1)}$) that could be associated to the interactions in a model defined on $n$ variables, selects a subset of $\mathcal{F} / {\sim}$ (see~\ref{fig:robustnessprocess}C)
\begin{equation}\label{eq:jacgrapheqs}
[G] = \left\{ [A] \; | \; G_A = G \right\}.
\end{equation}
The $G$-classes thereby partition the collection of fixed points, $\mathcal{F}$, over the space of dynamical systems, $\mathcal{D}$, according to the interactions among the variables of the dynamical system represented by the topology of $G$. This partition, $\mathcal{F} / G$, is a coarsening of $\mathcal{F} / {\sim}$.

>>>>

Each distinct labeled directed graph $G$ (of which there are $k=2^{n(n-1)}$) that could be associated to the interactions in a model defined on $n$ variables, selects a subset of $\mathcal{F} / {\sim}$ (see~\ref{fig:robustnessprocess}C)
\begin{equation}\label{eq:jacgrapheqs}
[G] = \left\{ [A] \; | \; G_A = G \right\}.
\end{equation}
The $G$-classes thereby partition the collection of fixed points, $\mathcal{F}$, over the space of dynamical systems, $\mathcal{D}$, according to the interactions among the variables of the dynamical system represented by the topology of $G$. This partition, $\mathcal{F} / G$, is a coarsening of $\mathcal{F} / {\sim}$. In what follows we consider the stability of classes of fixed points associated to each possible graph $G$. In most cases some of these are stable and some of them are unstable, which we quantify as the probability of stability. However, note that for some $G$, all fixed points respecting the topology of $G$ are unstable.
